\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage[a4paper, total={6in, 8in}]{geometry}

\newcommand{\answer}{\textbf{Answer:}$\;$}

\title{Sociology 141 Reading Guide 18}
\author{Alejandro Sanchez Ocegueda}
\date{April 3, 2025}

\begin{document}

\maketitle

\begin{enumerate}[label=\arabic*)]
    \item What does Behbehanian tell us about the state's raid of Occupy Oakland on the morning of October 25th? (pp. 64-66)
    
    \answer 
    We learn that it was very violent, and the police made use of militarize force.
    They used tear gas and ``less lethal'' ammunition to fire on the occupiers.
    They also raided the camp in the early morning in order to avoid alerting the press and the commuters nearby.
    
    \item What was the state's strategy in response to the movement's attempt to re-occupy Oscar Grant Plaza on the evening of October 25th? (pp. 67-68; 69-70)
    
    \answer 
    They applied even more violence, using tear gas and flash bangs.
    They were trying to keep the occupiers at bay, employing a strategy of ``Naked Coercion.''
    Their objective was to ``\textbf{contain}'' the Plaza.
    
    \item How does Behbehanian characterize the movement's strategic response to the October 25th raid? (pp. 74-75; 77-79)
   
    \answer
    They were persistent. 
    They refused to abandon their encampment and forced the state to use even more violence.
    This was all being done in order to make a spectacle out of the state, making sure that the images of police violence and brutality were being captured and disseminated to the world.
    
    \item Why does Behbehanian refer to the police shooting of Scott Olsen as the ``Achilles heel'' of the state's strategy? (pp. 74-75; 77-79)
    
    \answer 
    She refers to the shooting of Scott Olsen as the ``Achilles heel'' of the state's strategy because it was terrible press for the police.
    In their indiscriminate use of violence, they managed to shoot a young, White man who also happened to be a veteran; 
    in other words, they shot a person that the general public would care a great deal about.
    Furthermore, the whole scene was captured vividly on camera, which only led to massive amounts of outrage from the public.
    
    \item How does the ``spectacular backlash'' of the state's police operation on October 25th create a political opportunity for the movement?
    
    \answer
    Given that the October 25th raid was widely publicized and heavily criticized, the movement earned a lot of sympathy from the public view.
    This manifested in good press, donations, and endorsements from other Occupy movements and even artists like Lupe Fiasco.
    Moreover, they attracted more members, so the movement grew even larger after the state's attempt at repression than it was before.
    

    \item What was the state's strategy in response to Occupy Oakland's General Strike and Port Shutdown? (pp. 84-88)
    
    \answer
    Having learned from its mistakes, it attempted to make a more targeted use of force.
    They specifically targeted protesters that had taken over an abandoned public building in order to provide services for the homeless. 
    They initiated violence against these protesters, and they simultaneously branded them as rebels without a cause; opportunistic youth who were just trying to rebel.
    This was done in order to bring the police to a more favorable light in the eyes of the public.
    
    \item How did the state's second raid of Occupy Oakland on November 14th differ from its first raid attempt on October 25th? (pp. 91-93)
    
    \answer
    The main difference was that it was a lot less violent.
    They gave the protesters time to leave and refrained from using tear gas or beanbag ammo.
    This was part of a larger effort to disassociate the tactic of occupation from First Amendment protection.
    Their goal was to make the ``peaceful'' Occupiers the ones who did not occupy at all.
    
\end{enumerate}
 




\end{document}
